%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelance Senior Solution Architect} % Job title
    {1inch Limited} % Organization
    {Remote} % Location
    {Feb. 2023 - Okt. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed an API gateway written in GoLang able to handle 1.3 Billion requests per day}
        \item {Developed a low latency distributed rate limiter based on Redis Lua scripts}
        \item {Developed an Angular based developer portal with a Nest.js API backend}
        \item {Set up IaC using CDKTF/Terraform on AWS and Gitops in Kubernetes}
        \item {CI/CD pipeline setup using github actions}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Lead Engineer} % Job title
    {Porsche Digital GmbH} % Organization
    {Ludwigsburg, Germany} % Location
    {Sep. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team in developing high quality Vue.js frontend applications}
        \item {Contributed in designing the new architecture of the porsche.com website using JamStack (Astro, Vue, SSG)}
        \item {Implemented a proof of concept of the new target architecture based on CI/CD builds and CloudFront}
        \item {Implemented an MVP of the new Porsche adaptive stream video management platform (React, Cloudfront, HLS)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead - Data Streaming} % Job title
    {mimacom Deutschland GmbH} % Organization
    {Stuttgart, Germany} % Location
    {Sep. 2021 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Internal trainings and public training offering for Kafka}
        \item {Spoke in conferences about Kafka ALC management, Event Driven Architecture}
        \item {Design and creation of a low code PoC based on Kafka/ksqlDB and Next.js for a demo factory dashboard}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer / Solution Architect} % Job title
    {mimacom Deutschland GmbH} % Organization
    {Stuttgart, Germany} % Location
    {Jun. 2016 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitated MyPorsche cross team architectural discussions providing valuable input and opinions}
        \item {Designed and implemented an OpenCV based GIF generation software responsible for creating engaging personalized emails}
        \item {Driven the transformation of a monolith into Spring/Quarkus micro services communicating over Kafka to allow application scaling}
        \item {Bootstrapped and developed the official MyPorsche Inbox frontend customer application using Angular and GraphQL/DynamoDB/AWSLambda}
        \item {Set up distributed tracing via Opentracing and NewRelic to allow effective intra and cross team distributed tracing}
        \item {Set up CI/CD pipelines for automated build, test and continuous deployments to production}
        \item {Design and implementation of self managed API infrastructure on Azure via Pulumi}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Akera s.r.l.} % Organization
    {Venice, Italy} % Location
    {Nov. 2011 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented an explorer like interface in AngularJS for dynamic content}
        \item {Implemented a two layer cache based on aggregated hash keys using Varnish in Liferay 5.x}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
